Explore Vegetation Data

### 2015-06-30 explore_veg_data.Rmd
exported understory vegetation for 2005 and 2011 - complete sample years

veg_us_2011 <- filter(veg_us_summ, year == 2011)
veg_us_2005 <- filter(veg_us_summ, year < 2011)
```

>>>>

veg_us_2011 <- filter(veg_us_summ, year == 2011)
veg_us_2005 <- filter(veg_us_summ, year < 2011)

write.csv(veg_us_2005, "analysis/data/understory_veg_2005.csv")
write.csv(veg_us_2011, "analysis/data/understory_veg_2011.csv")
```
